  \begin{itemize}

\item[] M. Kvalheim, P. Gustafson, D. E. Koditschek, \href{https://arxiv.org/abs/2005.03217}{Conley's fundamental theorem for a class of hybrid systems}, arXiv:2005.03217.

\item[] J. Culbertson, P. Gustafson, D. E. Koditschek, P. F. Stiller, \href{http://www.tac.mta.ca/tac/volumes/35/45/35-45abs.html}{Formal composition of hybrid systems}, \emph{Theory and Applications of Categories} {35}, 2020, No. 45, 1634-1682.

  \item[] P. Gustafson, A. Kimball, E. C. Rowell, Q. Zhang, \href{https://arxiv.org/abs/1906.08153}{Braid group representations from twisted tensor products of algebras}, \emph{to appear in Peking Math. J.}, arXiv: 1906.08153.

  \item[]  A. Deaton, P. Gustafson, L. Mavrakis, E. C. Rowell., S. Poltoratski, S. Timmerman, B. Warren, Q. Zhang, \href{https://arxiv.org/abs/1901.04462}{Integral metaplectic modular categories}, \emph{J. Knot Theory Ramifications}, 29 (2020), no. 5, 2050032.
  
  \item[] P. Gustafson, E. C. Rowell, Y. Ruan, \href{https://arxiv.org/abs/1808.00698}{Metaplectic categories, gauging and Property F}, \emph{Tohoku Math. J.} {72} (2020) no. 3, 411-424.

  \item[] P. Bruillard, P. Gustafson, J. Plavnik, E. C. Rowell, \href{https://arxiv.org/abs/1710.10284}{Dimension as a quantum statistic and the classification of metaplectic categories}, in \emph{Topological phases of matter and quantum computation}, 89–113, Contemp. Math., 747, Amer. Math. Soc., Providence, RI, 2020.
    
  \item[] P. Gustafson, \href{https://arxiv.org/abs/1610.06069}{Finiteness for mapping class group representations from twisted Dijkgraaf-Witten theory}, \emph{J. Knot Theory Ramifications} 27 (2018) no. 6, 1850043.

  \item[] R. Fernandes, B. Li, K. Vadakkeveedu, A. Verma, P. Gustafson, et al., \href{http://proceedings.spiedigitallibrary.org/proceeding.aspx?articleid=1354959}{Agent-based analysis of trustworthiness in wireless sensor networks}, \emph{Proc. SPIE} {8407}, Multisensor, Multisource Information Fusion: Architectures, Algorithms, and Applications 2012, 84070W (May 1, 2012); doi:10.1117/12.920781. 

 \item[] P. Gustafson, N. Savir, E. Spears, \href{http://www.uni.edu/ajur/v5n3/Gufstafson\%20et\%20al\%20new\%20pp\%2011-20.pdf}{A characterization of refinable rational functions}, \emph{Am. J. Undergrad. Res.} {5} (3): 11-20 (Nov. 11, 2006).
  
 \end{itemize}
 
