% An introduction to Beamer created 6/8/2016
\documentclass{beamer}
\usetheme{Boadilla}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\usepackage{tikz}
\usepackage{hyperref}

\title{A Brief Introduction to LaTeX}
\author{Paul Gustafson (shamelessly stolen from Robert Williams)}
\institute{Texas A\&M University}
\date{June 2, 2017}

\begin{document}
	
	\begin{frame}
		\maketitle
	\end{frame}
	
	\begin{frame}{What is \LaTeX?}
		LaTeX (pronounced ``lay-tech'' or ``la-tech'') is type-setting software designed to satisfy technical and scientific needs.
		
		Why use it?
		\pause
		\begin{itemize}
			\item Your math looks nice \pause
			\item Customizable \pause
			\item Outputs pdf's \pause
			\item \alert<5>{The standard in scientific publication} \pause
		\end{itemize}
		
		\begin{exampleblock}{Downloading and Installing LaTeX}
			\url{http://latex-project.org/ftp.html}
		\end{exampleblock}
		\hyperlink{basic tex}{\beamerbutton{I'm new to LaTeX}}
		\quad
		\hyperlink{outline}{\beamerbutton{I'm familiar with LaTeX}}
		\quad
		\hyperlink{resources}{\beamerbutton{Take me to the resources
slide}}
	\end{frame}

        \begin{frame}{Article example}
          We'll go over two types of LaTeX files today: articles and beamer files.  The article document format is 
          used for writing papers.  The beamer format is used for writing presentations.
          
          \vfill
          
          Let's look at an example of an article.

          \vfill

        \end{frame}

	

	\begin{frame}[fragile]{Outline of a beamer file} \label{outline}
		\begin{verbatim}
		\documentclass[handout]{beamer} %handout collapses frames into
1 slide
		\usetheme{theme}
		\usecolortheme{color}
		
		\usepackage{amsmath, amsfonts, amssymb}
		\usepackage{tikz}
		
		\title{My Informative Title}
		\author{My Name}
		\institute{My Institution}
		\date{Date of presentation} or \date{\today}
		\end{verbatim}
	\end{frame}
	
	\begin{verbatim}
	
	
	
	
		\begin{document}
		
			\begin{frame}
				\maketitle
			\end{frame}
			
			\begin{frame}{Frame Title}
				Contents of paper or presentation
			\end{frame}
		
		\end{document}
	\end{verbatim}
	
	\begin{frame}{Beamer vs Article}
		Inside of each frame, you can write as you would in a normal LaTeX file. There is also a little bit of extra functionality present in beamer:
		\begin{itemize}
			\item You can give individual frames titles \pause
			\item You can segment frames into multiple slides using $\backslash$pause \pause
			\item You can create blocks to sort information \pause
			\item You can draw attention to points during some of these slides by using $\backslash$alert$\langle\#\rangle$\{text\}\pause
			\item You can separate a slide into multiple columns using the columns environment \pause
			\item You can create \hyperlink{outline}{\beamerbutton{hyperlinks}} to other parts of your presentation
		\end{itemize}
	\end{frame}
	
	\begin{frame}{Beamer example}
		The best way to learn beamer is to use it. Let's recreate the example beamer file.
        \end{frame}
                
	
	\begin{frame}{Basic Tex Reference} \label{basic tex}
		Symbols for type-setting commands:
		\begin{itemize}
			\item \% is used for comments
			\item $\backslash$ tells LaTeX you are writing a command
			\begin{itemize}
				\item some commands have \{inputs contained in curly brackets\} or [options contained in square braces]
			\end{itemize}
			\item \$ tells LaTeX to enter or exit math mode
		\end{itemize}
			
		\pause
			
		Common unintuitive commands:
		\begin{itemize}
			\item $\backslash\backslash$ is a line return
			\item \$\$ enters or exits display math mode
			\begin{itemize}
				\item Alternatively, $\backslash[ \text{ math goes here } \backslash]$ also uses display math mode
			\end{itemize}
		\end{itemize}		
	\end{frame}
	
	\begin{frame}[fragile]
		When in math mode, use \^~to write superscripts and \_ to write subscripts. Enclose the (super-)subscript in \{\} if it is more than 1 character long. \pause \\
		\begin{verbatim} $\sum_{n=1}^\infty \frac{1}{2^n} = 1$
\end{verbatim} $\sum_{n=1}^\infty \frac{1}{2^n} = 1$ \pause \\
		\begin{verbatim} $$\sum_{n=1}^\infty \frac{1}{2^n} = 1$$
\end{verbatim}
		$$\sum_{n=1}^\infty \frac{1}{2^n} = 1$$
	\end{frame}
	
	\begin{frame}[fragile]{Creating Lists}
		\begin{columns}
			\begin{column}{0.4\textwidth}
				\begin{verbatim}
					\begin{itemize}
						\item Item 1
						\item Item 2
					\end{itemize}
				\end{verbatim}
				\begin{itemize}
					\item Item 1
					\item Item 2
				\end{itemize}
			\end{column}
			\begin{column}{0.4\textwidth}
				\begin{verbatim}
					\begin{enumerate}
						\item Item 1
						\item Item 2
					\end{enumerate}
				\end{verbatim}
				\begin{enumerate}
					\item Item 1
					\item Item 2
				\end{enumerate}
			\end{column}
		\end{columns}
	\end{frame}
	
	\begin{frame}[fragile]{Tables and Matrices}
		\begin{columns}
			\begin{column}{0.4\textwidth}
				\begin{verbatim}
					\begin{tabular}{c|cc}
						a & b & c \\
						\hline
						d & e & f \\
						g & h & i
					\end{tabular}
				\end{verbatim}
				\begin{tabular}{c|cc}
					a & b & c \\
					\hline
					d & e & f \\
					g & h & i
				\end{tabular}
			\end{column}
			\begin{column}{0.4\textwidth}
				\begin{verbatim}
					$
					\begin{bmatrix}
					a & b & c \\
					d & e & f \\
					g & h & i 
					\end{bmatrix}
					$
				\end{verbatim}
				$
				\begin{bmatrix}
				a & b & c \\
				d & e & f \\
				g & h & i 
				\end{bmatrix}
				$
			\end{column}
		\end{columns}
	\end{frame}
	
	\begin{frame}[fragile]		
		\begin{verbatim}
		\begin{theorem}[Name/Attribution of Theorem]
		X iff Y
		\end{theorem}
		\end{verbatim}
		
		\begin{theorem}[Name/Attribution of Theorem]
			X iff Y
		\end{theorem}
		
		\begin{verbatim}
		\begin{proof}
		This is trivial.
		\end{proof}
		\end{verbatim}
		
		\begin{proof}
			This is trivial.
		\end{proof}
		
		\hyperlink{outline}{\beamerbutton{back to beamer}}
	\end{frame}
	
	% Resources Slide
	\begin{frame}{Additional Resources} \label{resources}
		LaTeX has an active community with many resources to help you along the way.
		\begin{itemize}
			\item LaTeX Wikibooks: \url{https://en.wikibooks.org/wiki/LaTeX}
			\item TeX Stack Exchange: \url{http://tex.stackexchange.com}
			\item The Not So Short Introduction to \LaTeXe:
\url{http://tobi.oetiker.ch/lshort/lshort.pdf}
			\item Detexify: \url{http://detexify.kirelabs.org/classify.html}
			\item A collection of beamer themes and colors:
\url{http://hartwork.org/beamer-theme-matrix/}
		\end{itemize}
	\end{frame}
	
\end{document}
